Pollution, agricultural productivity, and development: Evidence from coal plants in India

### 2023-04-13 presentation/slides/pollution-slides.Rmd
slides and readme

# Table
colnames(yield3ivmain) <- c("(1)", "(2)", "(3)")
rownames(yield3ivmain)[8] <- "F (first stage)"
kable(
      yield3ivmain,
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:4),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(7, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(labor3month) <- c("farm", "non-farm")
labor3month <- labor3month[-c(1:2, 13:14),]
labor3month <- labor3month[c(1:14),]
kable(
      labor3month,
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(14), hline_after = TRUE) %>%
  row_spec(c(12), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(yield4monthly) <- c("(1)", "(2)")
yield4monthly <- yield4monthly[c(1:14),]
kable(
      yield4monthly,
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(12, bold = TRUE) %>%
  row_spec(14, hline_after = TRUE) %>%
  kable_classic_2()

>>>>

# Table
yield3ivmain <- yield3ivmain[,-1]
colnames(yield3ivmain) <- c("(1)", "(2)", "(3)")
rownames(yield3ivmain)[8] <- "F (first stage)"
kable(
      yield3ivmain,
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:4),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(7, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(labor3month) <- c("farm", "non-farm")
kable(
      labor3month,
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(14), hline_after = TRUE) %>%
  row_spec(c(12), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(yield4monthly) <- c("(1)", "(2)")
yield4monthly <- yield4monthly[c(1:14, nrow(yield4monthly)),]
kable(
      yield4monthly,
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(12, bold = TRUE) %>%
  row_spec(14, hline_after = TRUE) %>%
  kable_classic_2()
